Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2021-11-04 _bookdown_files/06-conclusion.Rmd
Minor correction

Though we took a critic stance on the current literature, we still consider syndemic to be an useful framework to study the global health of marginalized populations and the current research still offered valuable insights on the health of MSM. It is up to scholars in the field to continue to push research forward in order to improve the health of marginalized populations worldwide.

>>>>

Though we took a critical stance on the current literature, we still consider syndemic to be an useful framework to study the global health of marginalized populations and the current research still offered valuable insights on the health of MSM. It is up to scholars in the field to continue to push research forward in order to improve the health of marginalized populations worldwide.
